A simple R markdown example}

### 2020-05-19 R/rmarkdown_fake.Rmd
update Fig 2 closes #39

---
title: "A simple R markdown example"
author: "Aaron Peikert & Andreas M. Brandmaier"
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: pdf_document
papersize: "a6"
geometry:
  - "landscape"
  - margin=0.5cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

@@

# Silly Heading

>>>>

---
title: "A simple R markdown example}"
author: "Aaron Peikert & Andreas M. Brandmaier"
output: pdf_document
---

### Silly Heading

@@
